Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a]{Bryan Quaife}
\author[a]{Ashley Gannon}
\author[b]{Howard A.~Stone}
\author[c,1]{Y.-N.~Young}

\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 32306}
\affil[b]{Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
\affil[c]{Department of Mathematical Sciences, New Jersey Institute of
Technology, Newark, NJ 07102}

@@

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Provided that the bilayer structure stays intact
without membrane poration or rupture under load, the water influx/efflux is
often assumed negligible in the absence of a gradient of osmotic
stress. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

>>>>

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a]{Bryan Quaife}
\author[a]{Ashley Gannon}
\author[b,1]{Y.-N.~Young}

\affil[a]{Department of Scientific Computing, Florida State University, Tallahessee, FL 32306}
\affil[b]{Department of Mathematical Sciences, New Jersey Institute of
Technology, Newark, NJ 07102}

@@

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Provided that the bilayer structure stays intact (no membrane poration or rupture) under load, the water influx/efflux is
often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}
